{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-30 bmvc_review.tex
Revised the section 2 a bit.

The order of deploying these three KCFs is critical as they need to run with full coherency to perfom robust tracking. The \textit{target+large background} translation filter, $R_{t}^{L}$, is designed to run in right next frame after the scale filter, $R_s$, which is applied at every $n=5$ frames. We deploy these two filters in this way because we want to minimize any drifts, which are likely to happen running only $R_{s}$. Finally, $R_{t}^{S}$ is applied in two consecutive frames before $R_{S}$ and right after two consecutive frames implementation of $R_{t}^{L}$. This way, we can integrate more discriminative shape features that can not be fully learned by $R_{t}^{L}$ as it contains contribution of large background in the learned model. On the other hand, $R_{t}^{L}$ uses shape and color information together to do a better job in recovering from any drifts due to application of $R_{s}$ in previous frame. In this framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$ and $R_{t}^{S}$ addresses the weakness of $R_{t}^{L}$ that it can not learn very useful shape features alone. Fig.~\ref{Workflow_figure_EnKCF} displays the proposed high-speed tracking framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of
the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.

@@

@@

\subsection{Particle Filter} \label{sc:PF}
The proposed {\it E}nKCF algorithm can cause undesired drift and noise in
tracking due to independent and less frequent application of the correlation filters. To
mitigate the drift effect further and reduce the noise, a Bayes Filter
representing the evolution of target's motion can be added into our
{\it E}nKCF tracking framework. To achieve this, we consider a variant of a
Bayes Filter, \textit{Particle Filter}. The Particle Filter is a
Sequential Monte Carlo method that uses a number of sample points to represent
the posterior probability density functions (pdf) of the target motion. 
The approximation becomes optimal with the infinite number of particles,
however, its run-time complexity grows exponentially with the number
of elements in the state space matrix, $X_{t}$. As the focus of this
study is to design a high speed tracker, we keep the number of state
space elements low and implement computationally efficient \textit{Weight
  Function} and \textit{Importance-Resampling} modules. We represent
the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$
where $x$ and $y$ are the centroid of the target and $V$ represents
the velocity components. We transit the particles with the first order Constant Velocity model. The centroid components are applied Gaussian Noise whereas the velocity components are assigned
uniform noise representative of most of the objects in our tests. The observation
likelihood is formulated based on the confidence map of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. 
The weights for the particles are computed as
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the size of the window in consideration. We can also use the spatial distance of particles to the peak of the confidence map, however, we believe that this approach could result in further drifts in the case of multi-modal distributions.

>>>>

The order of running these three KCFs is important as each of these
filters aims at addressing different chanllenges while perserving
run-time performance as fast as possible. The \textit{target+large
  background} translation filter, $R_{t}^{L}$, is intended to run
right after the scale filter, $R_s$, runs which is applied at every
$k=5$ frames. We run these two filters this way because we want to
minimize any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other frames
before $R_{S}$ and right after two consecutive frames running
$R_{t}^{L}$. By doing so, we can integrate more discriminative shape
features that can not be fully learned by $R_{t}^{L}$ as it contains
contribution of large background in the learned model. The filter,
$R_{t}^{L}$ uses shape and color information together to recover from
any potential drifts -- drifts could happen only looking the target's
scale by the filter, $R_{s}$.

{\it Burak: Rewrite the following paragraph.}

In summary, the filter, $R_{t}^{S}$, will handle the absence of scale
adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$
focuses on addressing the absence of translation estimation module in
$R_{S}$ and $R_{t}^{S}$ addresses the weakness of $R_{t}^{L}$ that it
can not learn very useful shape features
alone.

Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
proposed algorithm and Figure \ref{alg:MKCF} shows the pseudo-code of
{\it E}nKCF.

@@

{\it Burak: The KCF section doesn't fit the section before and
  after. In addition, it's still too long.}

@@

\subsection{Particle Filter} \label{sc:PF}
The proposed {\it E}nKCF algorithm can cause undesired drift and noise
in tracking due to independent and less frequent application of the
correlation filters.

{\it Burak: When we explain EnKCF, we've already used potential drifts
  are the reason why we want to have three KCFs. If we're talking
  about the same, kind of drifts, you have to be more careful. Having
  this section about particle filter will make it impractical or
  usefulness to have three KCFs.}

To mitigate the drift effect further and reduce the noise, a Bayes
Filter representing the evolution of target's motion can be added into
our {\it E}nKCF tracking framework. To achieve this, we consider a
variant of a Bayes Filter, \textit{Particle Filter}. The Particle
Filter is a Sequential Monte Carlo method that uses a number of sample
points to represent the posterior probability density functions (pdf)
of the target motion.  The approximation becomes optimal with the
infinite number of particles, however, its run-time complexity grows
exponentially with the number of elements in the state space matrix,
$X_{t}$. As the focus of this study is to design a high speed tracker,
we keep the number of state space elements low and implement
computationally efficient \textit{Weight Function} and
\textit{Importance-Resampling} modules. We represent the state space
matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$ where $x$ and $y$
are the centroid of the target and $V$ represents the velocity
components. We transit the particles with the first order Constant
Velocity model. The centroid components are applied Gaussian Noise
whereas the velocity components are assigned uniform noise
representative of most of the objects in our tests. The observation
likelihood is formulated based on the confidence map of $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$.  The weights for the particles are computed
as
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window in consideration. We can also use
the spatial distance of particles to the peak of the confidence map,
however, we believe that this approach could result in further drifts
in the case of multi-modal distributions.
